The \dealii Library, Version 9.5

### 2023-06-27 9.5/paper.tex
Update Kokkos section

In the current release, \texttt{LinearAlgebra::distributed::Vector} and the \texttt{CUDAWrappers::MatrixFree} framework are using \kokkos. This allows them to work on
all the architectures supported by \kokkos. The \kokkos backend used by \dealii is
\texttt{Kokkos::DefaultExecutionSpace} which is the highest available in the hierarchy
device, host-parallel, and host-serial.

\todo[inline]{Are you saying that all three of these are used? If so,
  maybe replace ``backend'' by ``backends''?}

\todo[inline]{Would it be useful to add a paragraph about future plans?}

>>>>

In the current release, \texttt{LinearAlgebra::distributed::Vector} and the 
\texttt{CUDAWrappers::MatrixFree} framework are using \kokkos. This allows them 
to work on all the architectures supported by \kokkos. The \kokkos backend used 
by \dealii is \texttt{Kokkos::DefaultExecutionSpace} which corresponds to the 
highest available backend in the hierarchy device, host-parallel, and host-serial 
at the time Kokkos was configured.
